---
title: "Network report"
output: html_document
params:
        ga: NA
        gs: NA
        node: NA
---

```{r, echo = FALSE, message = FALSE}
library(igraph)
library(ggplot2)
library(gridGraphics)
library(cowplot)
library(tidyverse)

id <- as.character(params$node)

color.pal <- function(pal = 'Greens', na.value = 0.5) {
    # replace missing with default value? with gray?
    function(x) {
        x[is.na(x)] <- na.value
        cr <- colorRamp(brewer.pal(9, pal), space='Lab')(x)
        #cr[is.na(cr)] <- 170
        rgb(cr[,1], cr[,2], cr[,3], maxColorValue = 255)
    }
}

plottable.g <- function(g) {
    #nbrs <- igraph::neighbors(g, params$node)
    # set node colors, labels, size
    V(g)$label <- ''
    V(g)$color <- color.pal()(0.3)
    V(g)$size <- 10
    # set you
    V(g)[name == id]$label <- 'You'
    V(g)[name == id]$color <- color.pal()(0.5)
    V(g)[name == id]$size <- 18
    # set neighbors
    V(g)[ .nei(id) ]$color <- color.pal()(0.5)
    V(g)[ .nei(id) ]$size <- 14
    g
}

g.stats <- function(g) {
    dat <- igraph::as_data_frame(g, 'vertices') %>%
        select(starts_with("centrality") | starts_with("name")) %>%
        select(!c(centrality.outdegree, centrality.indegree)) %>%
        rename(Eigenvector = centrality.eigen,
               Closeness = centrality.close,
               Betweenness = centrality.between,
               Cluster = centrality.cluster) %>%
        pivot_longer(!name, names_to = "centrality") %>%
        group_by(centrality) %>%
        mutate(pctile = rank(value) / n())
    dat
}

netplot <- function(g) {
    function() {
        plot(g,
             vertex.frame.color = 'white',
             vertex.label.family = 'sans',
             edge.color = '#aaaaaa',
             edge.width = 0.5,
             edge.curved = rep(0.25 * c(-1, 1), length.out = length(E(g))))
    }
}

pctile.plot <- function(g) {
    mp <- function(x) 0.5 * (max(x) + min(x))
    df <- g.stats(g)
    df.id <- df %>%
        mutate(pctile.label = sprintf('%0.1f%%', 100 * pctile)) %>%
        mutate(lab.h = ifelse(value < mp(value), -0.25, 1.25)) %>%
        filter(name == id)
    ggp <- df %>% ggplot(aes(value)) +
        theme_void() +
        theme(plot.margin = margin(0.3, 0, 0.3, 0, 'npc'),
              plot.title = element_text(margin = margin(0, 0, 0.1, 0, 'npc'))) +
        labs(x = NULL, y = NULL, title = 'Network Scores') +
        facet_wrap(~centrality, ncol = 1, scales = 'free') +
        geom_density(color = NA, fill = 'gray') +
        geom_vline(data = df.id, aes(xintercept = value)) +
        geom_text(data = df.id, aes(x = value, y = 0, label = pctile.label,
                                    hjust = lab.h), vjust = -1) +
        NULL
    ggp
}

```

This report presents a few different views of your position in the social
network of your class section. Keep in mind that the information it describes is
limited: it doesn't acknowledge your connections in your life outside INSEAD, or
even to others around the school. Network research does suggest, though, that
people's personalities tend to drive how they form ties with others, and that
people will tend to enter similar patterns of relationships throughout their
lives. As such, you should treat the results of this survey as one snapshot of
your life, and use it as an opportunity to reflect on how you approach social
situations.

Let's dive in:

# Advice network

As a reminder, the advice network asked if there was "anyone in the section from
whom you have regularly sought information and advice?" It is intended to
measure the extent to which people see each other as valuable professional
contacts.

```{r, echo = FALSE}
g <- plottable.g(params$ga)

plot_grid(netplot(g), pctile.plot(g), nrow = 1, rel_widths = c(3,1))
```

The left panel shows your position in the advice network and highlights your
direct ties. The right panel shows four measures of your position in the
network, including your percentile within the section (the percent of the
section with a lower score than you):

- *Betweenness centrality*: Betweenness centrality measures the extent to which
  you are a "bridge" between others in the network. It measures how many of the
  shortest paths between any two people in the network have to pass through you.
  Research suggests that people with a high betweenness centrality can
  synthesize different perspectives within a network, or even act as a
  matchmaker to bring people together.

- *Closeness centrality*: Closeness centrality measures how close you are to all
  other people in the network---it is your own "Kevin Bacon" score. People with
  a high closeness centrality are likely to quickly receive and send out
  information throughout a network.

- *Cluster centrality*: Clustering measures the fraction of your connections
  that are also connected to each other. People with a high clustering score
  tend to be members of a closely-connected group that can exert pressure and
  act cohesively in a network.

- *Eigenvector centrality*: Eigenvector centrality is often used to measure
  *status* or *prestige*. It measures the extent to which you are connected to
  other highly connected people. Even if you do not have many direct
  connections, you can have a high eigenvector score if your direct ties are
  themselves central.

# Social support network

As a reminder, the support network asked if there was "anyone in the section
whom you regard as a source of social support–that is, someone with whom you are
comfortable discussing sensitive matters?" It is intended to measure the extent
to which people see each other as confidantes or friends.

```{r, echo = FALSE}
g <- plottable.g(params$gs)

plot_grid(netplot(g), pctile.plot(g), nrow = 1, rel_widths = c(3,1))
```

The left panel shows your position in the support network and highlights your
direct ties. The right panel shows four measures of your position in the
network, including your percentile within the section (the percent of the
section with a lower score than you).

